Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-10-31 manuscript/manuscript.tex
add demographic descriptions
add new income graph
removing two graphs

\begin{table}[]
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lllllllllllllll}
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
  \textbf{Race}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
  \textbf{Ethnicity}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
  \textbf{Education}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  & 
  \end{tabular}%
  }
  \end{table}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{Income by year.pdf}
  \caption{Median Income by Year.}\label{fig:cars}
\end{figure}

\begin{figure}[tbp]
    \centering
    \includegraphics[width=\textwidth]{Income by town.pdf}
    \caption{Median Income by County.}\label{fig:cars}
  \end{figure}

@@

\subsubsection{Racial Disparities}
The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
targeted interventions addressing racial health inequalities. These disparities might be indicative of 
historical, social, and economic factors influencing the healthcare experiences of different racial groups.

>>>>

\ref{tab:Demographics}
\ref{fig:Income by County Graph}

\begin{table}[]
  \label{tab:Demographics}
  \caption{Demographics and Education Levels.}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lllllllllllllll}
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
  \textbf{Race (Percent)}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
  \textbf{Ethnicity (Percent)}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
  \textbf{Education (Percent)}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  & 
  \end{tabular}%
  }
  \end{table}

  \begin{figure}[tbp]
    \label{fig:Income by County Graph}
    \centering
    \includegraphics[width=\textwidth]{Income by County Graph.pdf}
    \caption{Median Income by County.}
  \end{figure}

@@

The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
targeted interventions addressing racial health inequalities. These disparities might be indicative of 
historical, social, and economic factors influencing the healthcare experiences of different racial groups.
